---
title: "Midterm"
knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'midterm.html'))})
output:
  html_document:
    toc: true
    toc_float: TRUE
    theme: cosmo
---

```{r,echo=F, message=F}
library(dplyr)
library(kableExtra)
library(emojifont)
library(ggplot2)
```

# W1D1: Jan. 4th, 2022 

- PHd in Statistics from Idaho

- Homework Due on Friday, and will be graded over the weekend. 

- Starting with Chapter 5.

- Class notes are in Canvas

CDF for two random variables have 3 properties

- smallest value is 0

- largest value is 1

- always non-decreasing 

Joint PMF for discrete variables uses summation and has two properties

- all probability are between 0 and 1

- total probability must be 1

Two way tables, because there are two ways to read it 

- also known as pivot table and contingency table

- make sure you can write and understand in different ways

O otherwise must be included for a complete distribution function. 

For PMF (discre rv) to be independent then, $p_{Y_1,Y_2}=p_1(y_1)\times p_2(y_2)$ for all $(y_1,y_2)$

- If $p_{Y_1,Y_2}\ne p_1(y_1)\times p_2(y_2)$ then NOT independent (meaning they are related to each other). 

**Complete first question of homework before next class.** 

```{r,echo=F, message=F, out.height = '30%', out.width = '40%', fig.align = "center" }
# smiley face emoji
# ggplot() + geom_emoji("smile", color='steelblue') + theme_void()
```


# W1D2: Jan. 6th, 2022

Review Homework will be Homework 1 and due Friday 14th 

## Joint PDF 

Properties :

1. smallest value is 0 

2. total volume under the joint pdf is 1

Notes : 

If the limits are given without equal sign then you can apply integral in the same way. 

The support is the area on the graph. 

Upper limit is only important for PMF of discrete random variables 

pdf : $f_{Y_1,Y_2}\geq0$

PMF : $0\leq p(y_1,y_2)\leq 1$

CDF : $F(y_1,y_2)=P(Y_1\leq y_1, Y_2\leq y_2)=\int_{-\infty}^{y_2}\int_{-\infty}^{y_1}f(y_1,y_2)dt_1dt_2$

- when we do problems we do not need to write every step of the integral 

- pay attention to the limits on the double integral ($y_1$ is on the inner intgegral, meaning it is integrated first ($dt_1$ inside $dt_2$))

- final answer will be a function, not a limit  

- lowest value must be 0, and highest value must be 1 

  - 0 otherwise is wrong without values for 1 included in CDF
  
- when you find the cdf you must use $dt_1$ and $dt_2$, but don't need it to use or solve for probabilities 
















# W2D3 :

# W2D4: 